---
title: "FML(R)"
author: "Nikitha Kotagiri"
date: "2023-09-10"
output:
  pdf_document: default
  html_document: default
---
# Imported the data set from kaggle
```{r}
make=read.csv("C:\\Users\\tirum\\Downloads\\archive\\Most Wickets in Test Cricket .csv")
make
```
# The below code shows descriptive statistics that includes qualitative and quantitative vafriables showing mean,median, mode and soon
```{r}
summary(make)
# qualitative variables
summary(make$Player)
summary(make$Country)
# quantitative variables
summary(make$Rank)
summary(make$Span)
summary(make$Matches)
summary(make$Innings)
summary(make$Runs)
summary(make$Wickets)
summary(make$Average)
summary(make$Econ)
```
#Transforming a new variable
```{r}
log_d= log(make$Wickets)
log_d
```
#I Plotted the graph with one quantitative variable in datset of make and the varible is Runs.
```{r}
 hist(make$Runs,main="Histogram of runs",col="green",border="black")
```


# Creating a scatter plot for the both quantitative and qualitative variable
```{r}
 x=make$Matches
y=make$Runs
plot(x,y)
```




